Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-08 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Updated educ section with png, small tweaks

	\begin{itemize_2pt}
		\item Targeting \textcolor{bdf}{specific subgroups} of the population
		\begin{itemize_2pt}
			\item Alleviating \textcolor{bdf}{particularly severe constraints}
			\item[] $\rightarrow$ Marginalized or disadvantaged groups (e.g., women, youth)
			\item  Maximizing \textcolor{bdf}{treatment impact} (or cost-effectiveness) 
			\item[] $\rightarrow$ Promising entrepreneurs (e.g., high-growth firms)

@@

\begin{frame}
\frametitle{Education and literacy}
\begin{itemize_2pt}
	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
	\vspace{0.1in}
\end{itemize_2pt}
\end{frame}

>>>>

	\begin{itemize_2pt}
		\item Targeting \textcolor{bdf}{specific subgroups} of the population
		\begin{itemize_2pt}
			\item Alleviating \textcolor{bdf}{particularly severe constraints}
			\item[] $\rightarrow$ Marginalized or disadvantaged groups (e.g., women, youth)
			\item  Maximizing \textcolor{bdf}{treatment impact} or cost-effectiveness 
			\item[] $\rightarrow$ Promising entrepreneurs (e.g., high-growth firms)

@@

\begin{frame}
\frametitle{Education and literacy}

Most MSE entrepreneurs have limited education

\vspace{-1.9em}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=27em]{pics/McK2017_educ.png}
	\label{McKenzie(2017): Education and cognitive functioning}
\end{figure}

\vspace{-2.5em}

\begin{itemize_2pt}
	\item Typical small-firm owner dropped out of highschool
	\item Test scores on digitspan and Raven's matrices about \% of Western university samples \textcolor{red}{\citep[comp.][]{}}
\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Education and literacy}

Potential for heuristics and rules of thumb
\begin{itemize_2pt}
	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
	\vspace{0.1in}
\end{itemize_2pt}
\end{frame}
